s\documentclass{cv}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage[sfdefault]{roboto}

\begin{document}
	\name{Corrina Sivak}
	
	\contact
		{\faEnvelopeSquare\space\href{mailto:csivak345@gmail.com}{csivak345@gmail.com}}
		{\faGithub\space\url{github.com/just-chillin}}
		{\faPhone\space\href{tel:14405031772}{(440) 503-1772}}
	
	\section{Objective}
	\begin{flushleft}
		I am a computer science student who is planning to finish classes in May. I am extremely excited about cloud computing and the business value that it can deliver. My goal is to graduate on a full time software engineering position or co-op in Summer 2021.
	\end{flushleft}

	
	\section{Skills}
	\textbf{Cloud Computing with AWS:} Elastic Beanstalk, EC2, Cognito, CloudFront, CodePipeline\newline
	\textbf{Languages:} JavaScript/TypeScript, Python, Java, Rust, Classwork Experience with Go and C++\newline
	\textbf{Data Structures and Algorithms}
	
	\section{Projects}
	\project{https://github.com/just-chillin/RustChip8Emulator}{RustChip8Emulator}{
	    An emulator built in Rust for the Chip-8 Virtual Machine. The Chip-8 was a microprocessor built in the mid 1970's for arcade cabinets and graphing calculators.
	}
	
	\project{https://github.com/just-chillin/RemixApp}{Remix}{
		TikTok like app built in React Native. Used S3 to store videos, Elastic Beanstalk to host the video retrieval API, and CloudFront to deliver the videos quickly. MongoDB Atlas was also used to host the video metadata. Backend was written with TypeScript and ExpressJS.
	}
	
	\project{https://github.com/just-chillin/ImageRunner}{ImageRunner}{
		Hackathon finalist project that used Google’s Cloud Vision API to interpret and run handwritten code. Used Python and Flask for the backend.
	}

	\section{Education}
	\datedsubsection{Rochester Institute of Technology}{Expected September 2021}
	BS in Computer Science

	\section{Experience}
	\job{CuraBox}{Remote}{Software Architect}{March-July 2020}
	\begin{itemize}
		\item Worked directly with designers to build UI using ReactJS and TypeScript
		\item Utilized AWS services such as EC2 and Elastic Beanstalk to host our APIs, as well as Cognito for authentication
		\item Designed secure backend APIs for retrieving customer data, authentication, and payment handling
		\item Handled data modeling and schema design for our MongoDB database
		\item Created CI pipelines using AWS CodePipeline to ensure a smooth deployment to production
	\end{itemize}

	\job{Red Argyle}{Rochester, NY}{Software Engineer}{June-December 2019}
	\begin{itemize}
		\item Leveraged Salesforce's robust ecosystem to do full stack development for companies like Google
		\item Built complex software for clients using agile methodology and scrum
		\item Directly worked with clients to gather technical requirements
		\item Ensured correct code using Salesforce's unit testing and code coverage suite
	\end{itemize}
\end{document} ​