\documentclass{cv}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage[sfdefault]{roboto}

\begin{document}
	\name{Corrina Sivak}
	
	\contact
		{\faEnvelopeSquare\space\href{mailto:csivak345@gmail.com}{csivak345@gmail.com}}
		{\faGithub\space\url{github.com/just-chillin}}
		{\faPhone\space\href{tel:14405031772}{(440) 503-1772}}
	
	\section{Summary}
	\begin{flushleft}
		I am a Software Engineer who will finish classes by June 1st. I am looking for a Backend or Full Stack Software Engineering Position at DataDog.
	\end{flushleft}

	
	\section{Skills}
	\textbf{Cloud Computing with AWS:} Elastic Beanstalk, EC2, Cognito, CloudFront, CodePipeline\newline
	\textbf{Programming Languages:} Rust, JavaScript/TypeScript, Python, Java, Go, C++\newline
	\textbf{Databases:} MongoDB, MySQL, DynamoDB\newline
	\textbf{Operating Systems:} Linux, Microsoft Windows, Apple MacOS\newline
	\textbf{Proficient in Object Oriented Design}\newline
	\textbf{Distributed Systems}\newline
	\textbf{Data Structures and Algorithms}
	
	\section{Projects}
	\project{https://github.com/just-chillin/RemixApp}{Remix}{
		TikTok like app built in React Native. Used S3 as data storage for videos, Elastic Beanstalk to host the video retrieval API, and CloudFront to deliver the videos quickly. MongoDB Atlas was also used to host the video metadata. Backend was written with TypeScript and ExpressJS.
	}
	
	\project{https://github.com/just-chillin/ImageRunner}{ImageRunner}{
		Innovative hackathon project that used Google’s Cloud Vision API to interpret and run handwritten code. Used Python and Flask for the backend. Had the opportunity to mentor others who were unfamiliar with software stack. Won 3rd place finalist in hackathon.
	}
	\project{https://github.com/willschneider15/Blendr}{Blendr}{
		Mobile app that helped cross-functional teams socialize. Built using React Native, and used firebase as backend. Utilized distributed systems concepts by finding ways to asynchronously match two employees together without the use of a message queue such as Kafka. Won 3rd place finalist in hackathon.
	}

	\section{Education}
	\datedsubsection{Rochester Institute of Technology}{Expected September 2021}
	BS in Computer Science

	\section{Experience}
	\job{CuraBox}{Remote}{Software Architect}{March-July 2020}
	\begin{itemize}
		\item Designed technical architecture and software development life cycle for main product
		\item Collaborated directly with designers to build UI using ReactJS and TypeScript
		\item Utilized scalable AWS services such as EC2 and Elastic Beanstalk to host our APIs, as well as Cognito for authentication
		\item Analyzed logs and metrics to investigate and solve issues in production
		\item Designed secure backend APIs for retrieving customer data, authentication, analytics, and payment handling
		\item Handled data modeling and schema design for data storage in MongoDB
		\item Saved time by creating CI pipelines using AWS CodePipeline
		\item Supervised a team of 2 other Software Engineers
	\end{itemize}

	\job{Red Argyle}{Rochester, NY}{Software Engineer}{June-December 2019}
	\begin{itemize}
		\item Leveraged Salesforce's robust ecosystem to do full stack development for companies like Google
		\item Utilized OO Design principles to build high quality code using Apex
		\item Delivered complex software for customers using agile methodology and scrum
		\item Directly worked with customers to gather technical requirements and problem solve current issues
		\item Wrote technical documentation for QA
		\item Ensured correct code using Salesforce's unit testing and code coverage suite
	\end{itemize}
\end{document} ​